---
title: "Definition Comparison"
author: "Sara Chronister, Maricopa County Department of Public Health"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

# install packages - only uncomment and run the following section (lines 12-18) your first time opening this
# install.packages("tidyverse")
# install.packages("jsonlite")
# install.packages("httr")
# install.packages("plotly")
# install.packages("eulerr")
# install.packages("reactable")
# install.packages("keyring")
# install.packages("ggraph")
# install.packages("igraph")
# install.packages("plyr")
# install.packages("widyr")
# install.packages("tidytext")


# load packages
library(tidyverse);library(jsonlite);library(httr);library(plotly);library(eulerr);library(reactable);library(readxl);library(plyr);library(widyr); library(tidytext);library(dplyr)
# keyring package to store/call usernames and passwords
library(keyring)

# leave the key_set lines commented out unless this is the first time running it
# if this is the first time running this script, uncomment the following lines, replace the username in the username = "" with your username for the respective services (local = computer, essence = ESSENCE), run the lines, enter your passwords for the respective services, and recomment the lines
# key_set(service = "local", username = "")
# key_set(service = "essence", username = "")

# IF your organization uses proxy settings, enter the information in the lines below and uncomment lines 33-36 (leave uncommented)
# look for proxy settings (windows) under settings > network and internet > proxy and look for the "Address" for url and "Port" for port
# the username and password are your network username and password, which you set in the key_set function above where service = "local"
# httr::set_config(use_proxy(url = "", # enter in the quotes
#                            port = 0000, # replace 0000 with your port number
#                            username = key_list("local")[1,2], 
#                            password = key_get("local", key_list("local")[1,2])))

source("SupportCode/Setup.R")

setup_information <- read_excel("Definition Comparison Table.xlsx", sheet = "Setup", range = "A2:C3")

query_start <- setup_information$StartDate
query_end <- setup_information$EndDate
jurisdiction <- setup_information$Jurisdiction

select_fields_table <- read_excel("Definition Comparison Table.xlsx", sheet = "AppliedFields", range = "A2:A22") %>%
  filter(!is.na(Field)) 
select_fields <- select_fields_table$Field

comparison_table <- read_excel("Definition Comparison Table.xlsx", sheet = "DefinitionInformation", range = "A2:H5")

```

```{r def1_setup, echo=FALSE, message=FALSE, warning=FALSE}

def1_table <- comparison_table[comparison_table$defX=="def1",]

def1_name <- def1_table$Syndrome
def1_short <- def1_table$Abbreviation
def1_diagnosis <- read_excel("Definition Comparison Table.xlsx", sheet = "Codes_Def1", range = "A4:C25") %>%
  filter(!is.na(DiagnosisCode))
def1_diagnosis_information <- ifelse(
  str_detect(def1_table$IncludeDiagnosisCode,"no|No|NO"),
  "This syndrome utilizes a large number of diagnosis code categories. Please see the full definition for specific codes.",
  reactable(def1_diagnosis))
def1_url <- def1_table$API

```

```{r def2_setup, echo=FALSE, message=FALSE, warning=FALSE}

def2_table <- comparison_table[comparison_table$defX=="def2",]

def2_name <- def2_table$Syndrome
def2_short <- def2_table$Abbreviation
def2_diagnosis <- read_excel("Definition Comparison Table.xlsx", sheet = "Codes_Def2", range = "A4:C25") %>%
  filter(!is.na(DiagnosisCode))
if (str_detect(def2_table$IncludeDiagnosisCode,"no|No|NO")) {
  def2_diagnosis_information <- "This syndrome utilizes a large number of diagnosis code categories. Please see the full definition for specific codes."
} else {
  def2_diagnosis_information <- reactable(def2_diagnosis, defaultPageSize = nrow(def2_diagnosis))
}
def2_url <- def2_table$API

```

```{r def3_setup, echo=FALSE, message=FALSE, warning=FALSE}

def3_table <- comparison_table[comparison_table$defX=="def3",]

def3_name <- def3_table$Syndrome
def3_short <- def3_table$Abbreviation
def3_diagnosis <- read_excel("Definition Comparison Table.xlsx", sheet = "Codes_Def3", range = "A4:C25") %>%
  filter(!is.na(DiagnosisCode))
if (str_detect(def3_table$IncludeDiagnosisCode,"no|No|NO")) {
  def3_diagnosis_information <- "This syndrome utilizes a large number of diagnosis code categories. Please see the full definition for specific codes."
} else {
  def3_diagnosis_information <- reactable(def3_diagnosis, defaultPageSize = nrow(def3_diagnosis))
}
def3_url <- def3_table$API

```

Syndrome Definitions: `r def1_name`, `r def2_name`, `r def3_name`  
Time Period: `r query_start` to `r query_end`   
Jurisdiction: `r jurisdiction`  


***  
### Syndrome Information  
  
#### `r def1_name` (`r def1_short`)   
  
* Fields applied to:  
    `r def1_table$Fields`   
* Description:  
    `r def1_table$Description`  
* Diagnostic Codes:   
    `r def1_diagnosis_information`   
* Query structure:  
    `r def1_table$Structure`     
* See ESSENCE for the full query text  

#### `r def2_name` (`r def2_short`)   
  
* Fields applied to:  
    `r def2_table$Fields`   
* Description:  
    `r def2_table$Description`  
* Diagnostic Codes:   
    `r def2_diagnosis_information`   
* Query structure:  
    `r def2_table$Structure`     
* See ESSENCE for the full query text  

#### `r def3_name` (`r def3_short`)   
  
* Fields applied to:  
    `r def3_table$Fields`   
* Description:  
    `r def3_table$Description`  
* Diagnostic Codes:   
    `r def3_diagnosis_information`   
* Query structure:  
    `r def3_table$Structure`     
* See ESSENCE for the full query text  
  
  
```{r def1_extract, echo=FALSE, message=FALSE, warning=FALSE}

def1_full <- return_longterm_query(url = def1_url, loop_start = query_start, loop_end = query_end)

def1 <- def1_full %>%
  dplyr::select(Date, EssenceID, select_fields) %>%
  mutate(def1 = 1)

```

```{r def2_extract, echo=FALSE, message=FALSE, warning=FALSE}

def2_full <- return_longterm_query(url = def2_url, loop_start = query_start, loop_end = query_end)

def2 <- def2_full %>%
  dplyr::select(Date, EssenceID, select_fields) %>%
  mutate(def2 = 1)

```

```{r def3_extract, echo=FALSE, message=FALSE, warning=FALSE}

def3_full <- return_longterm_query(url = def3_url, loop_start = query_start, loop_end = query_end)

def3 <- def3_full %>%
  dplyr::select(Date, EssenceID, select_fields) %>%
  mutate(def3 = 1)

```

```{r three_defs_prep, echo=FALSE, message=FALSE, warning=FALSE}

join_vars <- c("Date", "EssenceID", select_fields)

three_defs <- full_join(def1, def2, by = join_vars) %>%
  full_join(def3, by = join_vars) %>%
  replace_na(replace = list(def1 = 0, def2 = 0, def3 = 0)) %>%
  mutate(Total_Defs = def1+def2+def3)

three_defs_table <- three_defs %>%
  mutate(
    # Character values for definition indicator variables
    def1_named = factor(def1, levels = c(0,1), labels = c(paste("Not",def1_short), def1_short)),
    def2_named = factor(def2, levels = c(0,1), labels = c(paste("Not",def2_short), def2_short)),
    def3_named = factor(def3, levels = c(0,1), labels = c(paste("Not",def3_short), def3_short)),
    Total_Defs = factor(Total_Defs, levels = c(1,2,3), labels = c("One Definition", "Two Definitions", "Three Definitions")),
    # Dummy variables for each combination of definitions
    def1_only = ifelse(def1==1&def2==0&def3==0,1,0),
    def1_def2 = ifelse(def1==1&def2==1&def3==0,1,0),
    def1_def3 = ifelse(def1==1&def2==0&def3==1,1,0),
    def2_only = ifelse(def1==0&def2==1&def3==0,1,0),
    def2_def3 = ifelse(def1==0&def2==1&def3==1,1,0),
    def3_only = ifelse(def1==0&def2==0&def3==1,1,0),
    All = ifelse(def1==1&def2==1&def3==1,1,0))


three_defs_table$Definitions <- apply(three_defs_table[,c(11:13)], 1, function(data)
  paste(names(which(data == 1)),collapse = ", "))
three_defs_table$Definitions <- str_replace(three_defs_table$Definitions,"def1",def1_short)
three_defs_table$Definitions <- str_replace(three_defs_table$Definitions,"def2",def2_short)
three_defs_table$Definitions <- str_replace(three_defs_table$Definitions,"def3",def3_short)

```
  
  
***  
### Comparison Results  
  
#### The total number of visits identified by all queries combined was `r nrow(three_defs_table)`.   
  
*Number and percent of all identified visits captured by each definition:*     
```{r def_summary, echo=FALSE, message=FALSE, warning=FALSE}

def1_results <- data.frame(Def = def1_name, Count = sum(three_defs_table$def1)) %>%
  mutate(Percent = round(Count/nrow(three_defs_table),3),
         Percent.Display = paste0(Percent*100,"%"))

def2_results <- data.frame(Def = def2_name, Count = sum(three_defs_table$def2)) %>%
  mutate(Percent = round(Count/nrow(three_defs_table),3),
         Percent.Display = paste0(Percent*100,"%"))

def3_results <- data.frame(Def = def3_name, Count = sum(three_defs_table$def3)) %>%
  mutate(Percent = round(Count/nrow(three_defs_table),3),
         Percent.Display = paste0(Percent*100,"%"))

all_def_results <- bind_rows(def1_results, def2_results, def3_results)


ggplot(data = all_def_results, aes(x = Percent, y = reorder(Def,Percent))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=Count, x = Percent-.01), hjust="top", color = "white", size = 3) +
  geom_text(aes(label=Percent.Display, x = Percent+.01), hjust="bottom", color = "black", size = 3) +
  geom_segment(aes(x = 0, xend = 1, y = 0.4, yend = 0.4)) +
  scale_x_continuous(limits = c(0,1.2), expand = c(0,0), breaks = c(0,.25,.50,.75,1), labels = scales::percent_format()) +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")


```
  
*Number and percent of all identified visits captured by each observed combination of definitions:*     
  
```{r def_comparison, echo=FALSE, message=FALSE, warning=FALSE}

three_defs_combinations <- data.frame(Definitions = 
                                        c(paste(def1_short,def2_short,sep=", "),
                                          paste(def1_short,def3_short,sep=", "),
                                          paste(def2_short,def3_short,sep=", "),
                                          paste(def1_short,def2_short,def3_short,sep=", "),
                                          paste0(def1_short),
                                          paste0(def2_short),
                                          paste0(def3_short)))

three_defs_summary <- three_defs_table %>%
  dplyr::count(Definitions, name = "Visits") %>%
  mutate(Percent = paste0(round(Visits/sum(Visits)*100,1),"%")) %>%
  full_join(three_defs_combinations) %>%
  replace_na(list(Visits=0,
                  Percent="0%")) %>%
  arrange(desc(Visits))

reactable(three_defs_summary)

```

```{r rename_cols, echo=FALSE, message=FALSE, warning=FALSE}

Def1_vs_Def2_vs_Def3 <- three_defs
colnames(Def1_vs_Def2_vs_Def3)[11] <- def1_short
colnames(Def1_vs_Def2_vs_Def3)[12] <- def2_short
colnames(Def1_vs_Def2_vs_Def3)[13] <- def3_short

```
  
*Overlap of visits plotted to scale:*  
  
```{r euler, echo=FALSE, message=FALSE, warning=FALSE}

plot(euler(Def1_vs_Def2_vs_Def3[,11:13]),quantities = TRUE)

```
  
*Overlap of visits, not plotted to scale:*  
  
```{r venn, echo=FALSE, message=FALSE, warning=FALSE}

plot(venn(Def1_vs_Def2_vs_Def3[,11:13]))

```
  
  
***   
### Top term (besides "patient")
Top 5 occurring terms for each definition and each field of interest.

```{r word_prep, echo=FALSE, message = FALSE, warning = FALSE, results='hide'}

source("SupportCode/CleanFreeText.R")

my_file <- three_defs %>%
  mutate(Date = mdy(Date))

my_file <- clean_Admit_Reason_Combo()
my_file <- clean_ChiefComplaintOriginal()
my_file <- clean_ChiefComplaintUpdates()
my_file <- clean_ChiefComplaintParsed()
my_file <- clean_CCDD()
my_file <- clean_DischargeDiagnosis()


```


```{r top_terms, echo=FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=8}

def_sets <- list(my_file[my_file$def1==1,],
                 my_file[my_file$def2==1,],
                 my_file[my_file$def3==1,])

def_sets_names <- c(def1_short,def2_short,def3_short)

top_words <- list()
word_count <- list()

for (i in 1:length(def_sets)) {
  
  for(j in 1:length(select_fields)) {
    
    data <- as.data.frame(def_sets[i])
    
    field <- select_fields[j]
    
    word_count[[j]] <- data %>%
      dplyr::select(field) %>%
      unnest_tokens(word, !!field) %>%
      anti_join(stop_words, by = "word") %>%
      dplyr::count(word, name = "Count", sort=TRUE) %>%
      filter(word!="patient") %>%
      top_n(5) %>%
      mutate(def = def_sets_names[i],
             field = field)

    names(word_count)[[j]] <- select_fields[j]  
    
    }
  
  top_words[[i]] <- plyr::ldply(word_count, data.frame)

  names(top_words)[[i]] <- def_sets_names[i]
  
}

top_words_combined <- ldply(top_words, data.frame) %>%
  dplyr::arrange(Count) %>%
  group_by(def,field) %>%
  dplyr::mutate(order = row_number())

ggplot(data = top_words_combined) +
  geom_bar(aes(x = Count, y = as.factor(order)), stat="identity", fill = "#a4dba4") +
  geom_text(aes(x = 0, y = as.factor(order), label = paste0(word,'  (',Count,")"), hjust = "left"), size = 3) + 
  facet_grid(field ~ def, switch = "y", scales = "free") +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    panel.grid = element_blank(),
    strip.text.y.left = element_text(angle = 0),
    panel.background = element_rect(fill = NA, color = "grey40"),
    axis.title = element_blank()
  )

```

```{r output, echo=FALSE, message=FALSE, warning=FALSE}

# All Visits
write.csv(file = "Output/All Visits.csv",
          x = three_defs_table,
          row.names = FALSE)

# Def1 only
write.csv(file = paste0("Output/",def1_short," Only Visits.csv"),
          x = three_defs_table[three_defs_table$def1_only==1,],
          row.names = FALSE)

# Def2 only
write.csv(file = paste0("Output/",def2_short," Only Visits.csv"),
          x = three_defs_table[three_defs_table$def2_only==1,],
          row.names = FALSE)

# Def3 only
write.csv(file = paste0("Output/",def3_short," Only Visits.csv"),
          x = three_defs_table[three_defs_table$def3_only==1,],
          row.names = FALSE)

# Def1 and Def2 
write.csv(file = paste0("Output/",def1_short," and ",def2_short," Visits.csv"),
          x = three_defs_table[three_defs_table$def1_def2==1,],
          row.names = FALSE)

# Def1 and Def3 
write.csv(file = paste0("Output/",def1_short," and ",def3_short," Visits.csv"),
          x = three_defs_table[three_defs_table$def1_def3==1,],
          row.names = FALSE)

# Def2 and Def3 
write.csv(file = paste0("Output/",def2_short," and ",def3_short," Visits.csv"),
          x = three_defs_table[three_defs_table$def2_def3==1,],
          row.names = FALSE)


```










